1. Problem Statement

You are given the description of a city, represented by a bidimensional grid of
width W and height H.
On this grid, a series of buildings are positioned and your goal is to place
the available antennas in the best positions, according to requirements of each
building, in order to connect the city in the best way to the 5G ecosystem.

1.1. Building

A total of N buildings are already positioned on the grid, each of them in a
distinct location and needs connection.
As buildings are of various types also their connection needed can be different,
in particular each building characterized by the three factors:
• Its position on the grid.
• Latency weight: how important is the latency for the building.
• Connection speed weight: how important is the connection speed for
the building.

1.2. Antenna 

A total of M of antennas are available to be freely placed on the grid to give
connectivity to the neighborhood.
As also antennas can be of various types, each of them is characterized by two
factors:
• Range: the distance that the antenna signal can reach.
• Connection speed: the connection speed provided to the building connected to it.
Refer to the scoring section for the details.
Note that an antennas will provide the same ammount of connection speed to
all the buildings connected to it, regardless of the number of buildings.

1.3 Reward

As one of the goal of the 5G ecosystem is to reduce the digital divide, a
reward of R points will be assigned to the final score only if all the buildings
are connected to at least one antenna.

1.4 Input format

15 10  // Width and height of the grind
5 4 100 // number of building, antennas and quantity of reward if all building are connected
0 7 3 20 // coordinates (x,y),  latency weight and connection speed of the first building
12 2 2 14 
2 4 1 32 
10 7 4 44 
11 8 3 23 // last building info
2 100 // range and connection speed of the first antenna
4 10
1 50
2 40 // last antenna

1.5 Output format
// number of antennas placed
// M lines with (x,y) of the antenna coordinates with M the number of placed antenna